A Wide-Coverage Symbolic Natural Language Inference System

### 2019-03-01 paper2018/paper.tex
concluisions

\title{FraCaS: 80 percent complete}

@@

\section{Conclusions and Future Work}
We presented a system using  GF, Dynamic Semantics and Coq, essentially converting GF trees to Coq types using dynamic semantics. The system outperforms the state of the art in logical approaches when tested on the FraCaS test suite and is the only system to date that has performed a run on the ellipsis/anaphora section of the FraCaS. The system's precision  can form the start of a very precise NL reasoner for controlled domains. For the future, we plan to  extend the system to cover the remaining section of the FraCaS (tense/aspect), and also develop a more applied version to perform reasoning on controlled NL domains.

>>>>

\title{A Wide-Coverage Symbolic Natural Language Inference System}

@@

\section{Conclusions and Future Work}
We presented a system  converting GF trees to Coq types using dynamic semantics. The system outperforms the state of the art in logical approaches when tested on the FraCaS test suite and is the only system to date that has performed a run on the ellipsis/anaphora section of the FraCaS. The system is precise enough  to form the start of a very precise NL reasoner for controlled domains. For the future, we plan to  extend the system to cover the remaining section of the FraCaS (tense/aspect), and also develop a more applied version to perform reasoning on controlled NL domains.
